---
title: "TidyTuesday_2021-08-31"
author: "Nico Kosa"
date: "8/31/2021"
output: html_document
---

## Loading Libraries
```{r cars}
library(tidyverse)
```

## Reading in data
```{r cars}
bird_baths <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-08-31/bird_baths.csv')
```

## Quick Overview of Data
```{r cars}
summary(bird_baths)
```

## Data Organization/Preparation
```{r cars}
bird_regions <- bird_baths %>%
  group_by(bioregions, bird_type) %>%
  summarize(total_birds = sum(bird_count)) %>% 
  arrange(-total_birds, .by_group = TRUE) %>% 
  summarize(bird_type = first(bird_type), max = max(total_birds)) 

bird_regions %>% 
  drop_na()
```

## VIZ
```{r cars}
showtext_auto()
showtext_opts(dpi = 96)

ggplot(data = lemurs_tidy) + 
       geom_point(mapping = aes(x = age_rounded,
                                y = weight_g,
                                color = taxon)) +
  scale_fill_aaas() +
  theme_minimal() +
  labs(
    title = "Birdwalk Empire",
    subtitle = "Australian bird gangs and their main territories",
    caption = "@NkSmartbucks | Data: Cleary et al, 2016",
    x = "Age (y)",
    y = "Weight (g)"
  ) +
  theme(
    plot.title.position = "plot",
    plot.background = element_rect("snow3"),
    plot.title = element_text(family = "raleway", size = 20, face = "bold", vjust = 5, hjust = 1),
    plot.subtitle = element_text(family = "poppins", color = "gray30", hjust = -0.08, margin = margin(t = -15, b = 25)),
    axis.text = element_text(family = "poppins"),
    axis.title = element_text(family = "poppins"),
    axis.title.y = element_text(vjust = 100, margin = margin(r = 15)),
    axis.title.x = element_text(vjust = -5, margin = margin(t = 10)),
    plot.caption = element_text(family = "poppins", size = 8,
                                color = "gray30", hjust = -0.8, margin = margin(t = 20, b = -25)),
    panel.border = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
    plot.margin=unit(c(1,1,1,1), "cm"),
  )